Why do we Eval?\\[2mm]\Large A large-scale study of Eval usage in R

### 2020-11-26 inst/paper/main.tex
intro

\documentclass[USenglish,cleveref, autoref, thm-restate]{lipics-v2019}

\usepackage{listings}
\usepackage{hyperref}
\usepackage{multirow}
\usepackage{paralist}
\usepackage{xspace}
\usepackage{url}

\newcommand{\missingTag}[1]{\textcolor{red}{#1}\xspace}
\newcommand{\missingNumber}{\textcolor{red}{XX}\xspace}
\newcommand{\missingPercentage}{\textcolor{red}{XX\%}\xspace}
\newcommand{\missingTable}[1][XX]{\textcolor{red}{Table #1}\xspace}
\newcommand{\missingGraph}{\textcolor{red}{XXGraph}\xspace}

%\input{tag/counts.tex}
\newcommand{\CoreEvalCallCountRnd}{6.3M\xspace}
\newcommand{\CoreEvalCallCount}{6,282,429\xspace}
\newcommand{\CoreEvalSiteCountRnd}{185\xspace}
\newcommand{\CoreEvalSiteCount}{185\xspace}
\newcommand{\CoreEvalParentCallCountRnd}{186K\xspace}
\newcommand{\CoreEvalParentCallCount}{186,275\xspace}
\newcommand{\CoreEvalParentSiteCountRnd}{13\xspace}
\newcommand{\CoreEvalParentSiteCount}{13\xspace}
\newcommand{\CoreEvalqCallCountRnd}{132K\xspace}
\newcommand{\CoreEvalqCallCount}{132,891\xspace}
\newcommand{\CoreEvalqSiteCountRnd}{20K\xspace}
\newcommand{\CoreEvalqSiteCount}{20,460\xspace}
\newcommand{\CoreLocalCallCountRnd}{175K\xspace}
\newcommand{\CoreLocalCallCount}{175,079\xspace}
\newcommand{\CoreLocalSiteCountRnd}{920\xspace}
\newcommand{\CoreLocalSiteCount}{920\xspace}
\newcommand{\PackageEvalCallCountRnd}{1.6M\xspace}
\newcommand{\PackageEvalCallCount}{1,582,738\xspace}
\newcommand{\PackageEvalSiteCountRnd}{1.5K\xspace}
\newcommand{\PackageEvalSiteCount}{1,459\xspace}
\newcommand{\PackageEvalParentCallCountRnd}{13K\xspace}
\newcommand{\PackageEvalParentCallCount}{13,230\xspace}
\newcommand{\PackageEvalParentSiteCountRnd}{249\xspace}
\newcommand{\PackageEvalParentSiteCount}{249\xspace}
\newcommand{\PackageEvalqCallCountRnd}{2\xspace}
\newcommand{\PackageEvalqCallCount}{2\xspace}
\newcommand{\PackageEvalqSiteCountRnd}{1\xspace}
\newcommand{\PackageEvalqSiteCount}{1\xspace}
\newcommand{\PackageLocalCallCountRnd}{2.2K\xspace}
\newcommand{\PackageLocalCallCount}{2,228\xspace}
\newcommand{\PackageLocalSiteCountRnd}{15\xspace}
\newcommand{\PackageLocalSiteCount}{15\xspace}
\newcommand{\KaggleEvalCallCountRnd}{0\xspace}
\newcommand{\KaggleEvalCallCount}{0\xspace}
\newcommand{\KaggleEvalSiteCountRnd}{0\xspace}
\newcommand{\KaggleEvalSiteCount}{0\xspace}
\newcommand{\KaggleEvalParentCallCountRnd}{0\xspace}
\newcommand{\KaggleEvalParentCallCount}{0\xspace}
\newcommand{\KaggleEvalParentSiteCountRnd}{0\xspace}
\newcommand{\KaggleEvalParentSiteCount}{0\xspace}
\newcommand{\KaggleEvalqCallCountRnd}{0\xspace}
\newcommand{\KaggleEvalqCallCount}{0\xspace}
\newcommand{\KaggleEvalqSiteCountRnd}{0\xspace}
\newcommand{\KaggleEvalqSiteCount}{0\xspace}
\newcommand{\KaggleLocalCallCountRnd}{0\xspace}
\newcommand{\KaggleLocalCallCount}{0\xspace}
\newcommand{\KaggleLocalSiteCountRnd}{0\xspace}
\newcommand{\KaggleLocalSiteCount}{0\xspace}
\newcommand{\CoreAllCallCountRnd}{6.8M\xspace}
\newcommand{\CoreAllCallCount}{6,776,674\xspace}
\newcommand{\CoreAllSiteCountRnd}{21.6K\xspace}
\newcommand{\CoreAllSiteCount}{21,578\xspace}
\newcommand{\KaggleAllCallCountRnd}{0\xspace}
\newcommand{\KaggleAllCallCount}{0\xspace}
\newcommand{\KaggleAllSiteCountRnd}{0\xspace}
\newcommand{\KaggleAllSiteCount}{0\xspace}
\newcommand{\PackageAllCallCountRnd}{1.6M\xspace}
\newcommand{\PackageAllCallCount}{1,598,198\xspace}
\newcommand{\PackageAllSiteCountRnd}{1.7K\xspace}
\newcommand{\PackageAllSiteCount}{1,724\xspace}
\newcommand{\AllEvalCallCountRnd}{7.9M\xspace}
\newcommand{\AllEvalCallCount}{7,865,167\xspace}
\newcommand{\AllEvalSiteCountRnd}{1.6K\xspace}
\newcommand{\AllEvalSiteCount}{1,644\xspace}
\newcommand{\AllEvalParentCallCountRnd}{199.5K\xspace}
\newcommand{\AllEvalParentCallCount}{199,505\xspace}
\newcommand{\AllEvalParentSiteCountRnd}{262\xspace}
\newcommand{\AllEvalParentSiteCount}{262\xspace}
\newcommand{\AllEvalqCallCountRnd}{132.9K\xspace}
\newcommand{\AllEvalqCallCount}{132,893\xspace}
\newcommand{\AllEvalqSiteCountRnd}{20.5K\xspace}
\newcommand{\AllEvalqSiteCount}{20,461\xspace}
\newcommand{\AllLocalCallCountRnd}{177.3K\xspace}
\newcommand{\AllLocalCallCount}{177,307\xspace}
\newcommand{\AllLocalSiteCountRnd}{935\xspace}
\newcommand{\AllLocalSiteCount}{935\xspace}
\newcommand{\AllAllCallCountRnd}{8.4M\xspace}
\newcommand{\AllAllCallCount}{8,374,872\xspace}
\newcommand{\AllAllSiteCountRnd}{23.3K\xspace}
\newcommand{\AllAllSiteCount}{23,302\xspace}
\newcommand{\TotalFileCountRnd}{18.3K\xspace}
\newcommand{\TotalFileCount}{18,258\xspace}
\newcommand{\NoEvalFileCountRnd}{89\xspace}
\newcommand{\NoEvalFileCount}{89\xspace}
\newcommand{\NoEvalFilePerc}{0.5\%\xspace}
\newcommand{\CoreEvalFileCountRnd}{12.3K\xspace}
\newcommand{\CoreEvalFileCount}{12,307\xspace}
\newcommand{\CoreEvalFilePerc}{67.4\%\xspace}
\newcommand{\PackageEvalFileCountRnd}{0\xspace}
\newcommand{\PackageEvalFileCount}{0\xspace}
\newcommand{\PackageEvalFilePerc}{0\%\xspace}
\newcommand{\AllEvalFileCountRnd}{5.9K\xspace}
\newcommand{\AllEvalFileCount}{5,862\xspace}
\newcommand{\AllEvalFilePerc}{32.1\%\xspace}
\newcommand{\EightyCoreEvalFileCountRnd}{3.8K\xspace}
\newcommand{\EightyCoreEvalFileCount}{3,769\xspace}
\newcommand{\EightyCoreEvalFilePerc}{64.3\%\xspace}
\newcommand{\TopTenPackageCallCountRnd}{1.4M\xspace}
\newcommand{\TopTenPackageCallCount}{1,425,902\xspace}
\newcommand{\TopTenPackageCallPerc}{89.2\%\xspace}
\newcommand{\TopTenPackageSiteCountRnd}{282\xspace}
\newcommand{\TopTenPackageSiteCount}{282\xspace}
\newcommand{\TopTenPackageSitePerc}{16\%\xspace}
\newcommand{\TopTenPackageNameA}{ggplot2\xspace}
\newcommand{\TopTenPackageCallsiteCountARnd}{2\xspace}
\newcommand{\TopTenPackageCallsiteCountA}{2\xspace}
\newcommand{\TopTenPackageCallCountARnd}{987K\xspace}
\newcommand{\TopTenPackageCallCountA}{987,946\xspace}
\newcommand{\TopTenPackageCallPercA}{61\%\xspace}
\newcommand{\TopTenPackageNameB}{magrittr\xspace}
\newcommand{\TopTenPackageCallsiteCountBRnd}{5\xspace}
\newcommand{\TopTenPackageCallsiteCountB}{5\xspace}
\newcommand{\TopTenPackageCallCountBRnd}{139K\xspace}
\newcommand{\TopTenPackageCallCountB}{139,346\xspace}
\newcommand{\TopTenPackageCallPercB}{8.7\%\xspace}
\newcommand{\TopTenPackageNameC}{plyr\xspace}
\newcommand{\TopTenPackageCallsiteCountCRnd}{11\xspace}
\newcommand{\TopTenPackageCallsiteCountC}{11\xspace}
\newcommand{\TopTenPackageCallCountCRnd}{68K\xspace}
\newcommand{\TopTenPackageCallCountC}{68,671\xspace}
\newcommand{\TopTenPackageCallPercC}{4.3\%\xspace}
\newcommand{\TopTenPackageNameD}{glue\xspace}
\newcommand{\TopTenPackageCallsiteCountDRnd}{5\xspace}
\newcommand{\TopTenPackageCallsiteCountD}{5\xspace}
\newcommand{\TopTenPackageCallCountDRnd}{62K\xspace}
\newcommand{\TopTenPackageCallCountD}{62,564\xspace}
\newcommand{\TopTenPackageCallPercD}{3.9\%\xspace}
\newcommand{\TopTenPackageNameE}{data.table\xspace}
\newcommand{\TopTenPackageCallsiteCountERnd}{31\xspace}
\newcommand{\TopTenPackageCallsiteCountE}{31\xspace}
\newcommand{\TopTenPackageCallCountERnd}{47K\xspace}
\newcommand{\TopTenPackageCallCountE}{47,464\xspace}
\newcommand{\TopTenPackageCallPercE}{3\%\xspace}
\newcommand{\TopTenPackageNameF}{statnet.common\xspace}
\newcommand{\TopTenPackageCallsiteCountFRnd}{12\xspace}
\newcommand{\TopTenPackageCallsiteCountF}{12\xspace}
\newcommand{\TopTenPackageCallCountFRnd}{30K\xspace}
\newcommand{\TopTenPackageCallCountF}{30,581\xspace}
\newcommand{\TopTenPackageCallPercF}{1.9\%\xspace}
\newcommand{\TopTenPackageNameG}{VGAM\xspace}
\newcommand{\TopTenPackageCallsiteCountGRnd}{97\xspace}
\newcommand{\TopTenPackageCallsiteCountG}{97\xspace}
\newcommand{\TopTenPackageCallCountGRnd}{23K\xspace}
\newcommand{\TopTenPackageCallCountG}{23,796\xspace}
\newcommand{\TopTenPackageCallPercG}{1.5\%\xspace}
\newcommand{\TopTenPackageNameH}{copula\xspace}
\newcommand{\TopTenPackageCallsiteCountHRnd}{21\xspace}
\newcommand{\TopTenPackageCallsiteCountH}{21\xspace}
\newcommand{\TopTenPackageCallCountHRnd}{22K\xspace}
\newcommand{\TopTenPackageCallCountH}{22,794\xspace}
\newcommand{\TopTenPackageCallPercH}{1.4\%\xspace}
\newcommand{\TopTenPackageNameI}{nlme\xspace}
\newcommand{\TopTenPackageCallsiteCountIRnd}{97\xspace}
\newcommand{\TopTenPackageCallsiteCountI}{97\xspace}
\newcommand{\TopTenPackageCallCountIRnd}{21K\xspace}
\newcommand{\TopTenPackageCallCountI}{21,483\xspace}
\newcommand{\TopTenPackageCallPercI}{1.3\%\xspace}
\newcommand{\TopTenPackageNameJ}{R6\xspace}
\newcommand{\TopTenPackageCallsiteCountJRnd}{1\xspace}
\newcommand{\TopTenPackageCallsiteCountJ}{1\xspace}
\newcommand{\TopTenPackageCallCountJRnd}{21K\xspace}
\newcommand{\TopTenPackageCallCountJ}{21,257\xspace}
\newcommand{\TopTenPackageCallPercJ}{1.3\%\xspace}

\input{tag/corpus.tex}
%\input{tag/side-effects.tex}
\newcommand{\AllWritesRnd}{9.4G\xspace}
\newcommand{\AllWrites}{9,427,046,091\xspace}
\newcommand{\EvalWritesRnd}{1.1G\xspace}
\newcommand{\EvalWrites}{1,065,212,013\xspace}
\newcommand{\EvalSideEffectingWritesRnd}{45M\xspace}
\newcommand{\EvalSideEffectingWrites}{45,701,209\xspace}
\newcommand{\EvalSideEffectingWritesEvalPerc}{4.3\%\xspace}
\newcommand{\EvalSideEffectingWritesAllPerc}{.5\%\xspace}
\newcommand{\SideEffectingCoreCallPerc}{4.4\%\xspace}
\newcommand{\SideEffectingPackageCallPerc}{7.5\%\xspace}

%\input{tag/operations.tex}
\newcommand{\AllValueInputEvalCallPerc}{17\%\xspace}
\newcommand{\AllExpressionInputEvalCallPerc}{82\%\xspace}
\newcommand{\AllExpressionInputEvalSitePerc}{14\%\xspace}
\newcommand{\AllValueInputEvalSitePerc}{3\%\xspace}
\newcommand{\AllPolymorphicInputEvalSitePerc}{82\%\xspace}
\newcommand{\PackageEnvironmentInputEvalCallPerc}{62\%\xspace}
\newcommand{\AllClosureCallCountRnd}{2.9G\xspace}
\newcommand{\AllClosureCallCount}{2,886,992,072\xspace}
\newcommand{\EvalClosureCallCountRnd}{125M\xspace}
\newcommand{\EvalClosureCallCount}{125,469,701\xspace}
\newcommand{\AllNativeCallCountRnd}{463M\xspace}
\newcommand{\AllNativeCallCount}{463,803,879\xspace}
\newcommand{\EvalNativeCallCountRnd}{31M\xspace}
\newcommand{\EvalNativeCallCount}{31,164,219\xspace}

%\input{tag/events.tex}
\newcommand{\AllEventCountRnd}{39G\xspace}
\newcommand{\AllEventCount}{38,991,360,760\xspace}
\newcommand{\EvalEventCountRnd}{2G\xspace}
\newcommand{\EvalEventCount}{1,973,736,718\xspace}
\newcommand{\EventsMaxCountRnd}{17M\xspace}
\newcommand{\EventsMaxCount}{17,656,694\xspace}
\newcommand{\EvalEventAllPerc}{5\%\xspace}
\newcommand{\EventsMinRangeARnd}{0\xspace}
\newcommand{\EventsMinRangeA}{0\xspace}
\newcommand{\EventsMaxRangeARnd}{100\xspace}
\newcommand{\EventsMaxRangeA}{100\xspace}
\newcommand{\EventsCoreEvalCountARnd}{5M\xspace}
\newcommand{\EventsCoreEvalCountA}{5,659,053\xspace}
\newcommand{\EventsCoreEvalPercA}{88\%\xspace}
\newcommand{\EventsPackageEvalCountARnd}{1.5M\xspace}
\newcommand{\EventsPackageEvalCountA}{1,514,222\xspace}
\newcommand{\EventsPackageEvalPercA}{93\%\xspace}
\newcommand{\EventsMinRangeBRnd}{101\xspace}
\newcommand{\EventsMinRangeB}{101\xspace}
\newcommand{\EventsMaxRangeBRnd}{10K\xspace}
\newcommand{\EventsMaxRangeB}{10,000\xspace}
\newcommand{\EventsCoreEvalCountBRnd}{769K\xspace}
\newcommand{\EventsCoreEvalCountB}{769,341\xspace}
\newcommand{\EventsCoreEvalPercB}{12\%\xspace}
\newcommand{\EventsPackageEvalCountBRnd}{100K\xspace}
\newcommand{\EventsPackageEvalCountB}{100,141\xspace}
\newcommand{\EventsPackageEvalPercB}{6\%\xspace}
\newcommand{\EventsMinRangeCRnd}{10K\xspace}
\newcommand{\EventsMinRangeC}{10,001\xspace}
\newcommand{\EventsMaxRangeCRnd}{20M\xspace}
\newcommand{\EventsMaxRangeC}{20,000,000\xspace}
\newcommand{\EventsCoreEvalCountCRnd}{3K\xspace}
\newcommand{\EventsCoreEvalCountC}{2,997\xspace}
\newcommand{\EventsCoreEvalPercC}{0\%\xspace}
\newcommand{\EventsPackageEvalCountCRnd}{14K\xspace}
\newcommand{\EventsPackageEvalCountC}{14,209\xspace}
\newcommand{\EventsPackageEvalPercC}{.9\%\xspace}

%\input{tag/analysisStable.tex}
\newcommand{\UniqueCallsRnd}{1.3M\xspace}
\newcommand{\UniqueCalls}{1,277,948\xspace}
\newcommand{\MatchArgNumberRnd}{5M\xspace}
\newcommand{\MatchArgNumber}{5,029,351\xspace}
\newcommand{\MatchArgPercent}{60\%\xspace}
\newcommand{\NbAstOnePercent}{15\%\xspace}
\newcommand{\NbAstOneCallSitePercent}{96\%\xspace}
\newcommand{\AstSizeNineFiveRnd}{42\xspace}
\newcommand{\AstSizeNineFive}{42\xspace}
\newcommand{\AstSizeNineFiveExactPercent}{95\%\xspace}
\newcommand{\DefaultEnvirExprRnd}{1.1M\xspace}
\newcommand{\DefaultEnvirExpr}{1,054,124\xspace}
\newcommand{\DefaultEnvirExprPercent}{12\%\xspace}
\newcommand{\DefaultEnvirCallSitesPercent}{9.3\%\xspace}
\newcommand{\DefaultEnvirCoreExprPercent}{10\%\xspace}
\newcommand{\DefaultEnvirPackagesExprPercent}{20\%\xspace}
\newcommand{\CoreEnvClassA}{2\xspace}
\newcommand{\CoreCountARnd}{5M\xspace}
\newcommand{\CoreCountA}{5,079,433\xspace}
\newcommand{\CoreProportionA}{83\%\xspace}
\newcommand{\CoreEnvClassB}{list\xspace}
\newcommand{\CoreCountBRnd}{229K\xspace}
\newcommand{\CoreCountB}{229,249\xspace}
\newcommand{\CoreProportionB}{3.8\%\xspace}
\newcommand{\CoreEnvClassC}{3\xspace}
\newcommand{\CoreCountCRnd}{199K\xspace}
\newcommand{\CoreCountC}{199,497\xspace}
\newcommand{\CoreProportionC}{3.3\%\xspace}
\newcommand{\CoreEnvClassD}{global+\xspace}
\newcommand{\CoreCountDRnd}{183K\xspace}
\newcommand{\CoreCountD}{183,631\xspace}
\newcommand{\CoreProportionD}{3\%\xspace}
\newcommand{\CoreEnvClassE}{1+\xspace}
\newcommand{\CoreCountERnd}{175K\xspace}
\newcommand{\CoreCountE}{175,151\xspace}
\newcommand{\CoreProportionE}{2.9\%\xspace}
\newcommand{\CoreEnvClassF}{global\xspace}
\newcommand{\CoreCountFRnd}{124K\xspace}
\newcommand{\CoreCountF}{124,673\xspace}
\newcommand{\CoreProportionF}{2.1\%\xspace}
\newcommand{\CoreEnvClassG}{sys.call(sys.parent())\xspace}
\newcommand{\CoreCountGRnd}{32K\xspace}
\newcommand{\CoreCountG}{32,349\xspace}
\newcommand{\CoreProportionG}{.5\%\xspace}
\newcommand{\CoreEnvClassH}{loop\xspace}
\newcommand{\CoreCountHRnd}{24K\xspace}
\newcommand{\CoreCountH}{24,286\xspace}
\newcommand{\CoreProportionH}{.4\%\xspace}
\newcommand{\PackagesEnvClassA}{global+\xspace}
\newcommand{\PackagesCountARnd}{943K\xspace}
\newcommand{\PackagesCountA}{943,682\xspace}
\newcommand{\PackagesProportionA}{74\%\xspace}
\newcommand{\PackagesEnvClassB}{3\xspace}
\newcommand{\PackagesCountBRnd}{71K\xspace}
\newcommand{\PackagesCountB}{71,037\xspace}
\newcommand{\PackagesProportionB}{5.6\%\xspace}
\newcommand{\PackagesEnvClassC}{2\xspace}
\newcommand{\PackagesCountCRnd}{67K\xspace}
\newcommand{\PackagesCountC}{67,555\xspace}
\newcommand{\PackagesProportionC}{5.3\%\xspace}
\newcommand{\PackagesEnvClassD}{5\xspace}
\newcommand{\PackagesCountDRnd}{49K\xspace}
\newcommand{\PackagesCountD}{49,782\xspace}
\newcommand{\PackagesProportionD}{3.9\%\xspace}
\newcommand{\PackagesEnvClassE}{list\xspace}
\newcommand{\PackagesCountERnd}{44K\xspace}
\newcommand{\PackagesCountE}{44,194\xspace}
\newcommand{\PackagesProportionE}{3.5\%\xspace}
\newcommand{\PackagesEnvClassF}{2+\xspace}
\newcommand{\PackagesCountFRnd}{32K\xspace}
\newcommand{\PackagesCountF}{32,931\xspace}
\newcommand{\PackagesProportionF}{2.6\%\xspace}
\newcommand{\PackagesEnvClassG}{global\xspace}
\newcommand{\PackagesCountGRnd}{22K\xspace}
\newcommand{\PackagesCountG}{22,825\xspace}
\newcommand{\PackagesProportionG}{1.8\%\xspace}
\newcommand{\PackagesEnvClassH}{base+\xspace}
\newcommand{\PackagesCountHRnd}{18K\xspace}
\newcommand{\PackagesCountH}{18,538\xspace}
\newcommand{\PackagesProportionH}{1.5\%\xspace}
\newcommand{\NbEnclosEnvirRnd}{274K\xspace}
\newcommand{\NbEnclosEnvir}{274,370\xspace}
\newcommand{\EnclosEnvirPercent}{3.3\%\xspace}
\newcommand{\NbSysCallEnvirRnd}{33K\xspace}
\newcommand{\NbSysCallEnvir}{33,650\xspace}
\newcommand{\SysCallEnvirPercent}{.4\%\xspace}
\newcommand{\NbMonomorphicRnd}{23.1K\xspace}
\newcommand{\NbMonomorphic}{23,069\xspace}
\newcommand{\PercentMonomorphic}{99\%\xspace}
\newcommand{\PercentParsedEvals}{.9\%\xspace}
\newcommand{\PercentParsedCallSites}{1\%\xspace}
\newcommand{\NbParseFilesRnd}{10\xspace}
\newcommand{\NbParseFiles}{10\xspace}
\newcommand{\PercentParseFileCallSites}{.01\%\xspace}
\newcommand{\PasteParsedEvals}{39\%\xspace}
\newcommand{\PasteParsedCallSite}{51\%\xspace}
\newcommand{\NbCoreEvalCallSitesRnd}{310\xspace}
\newcommand{\NbCoreEvalCallSites}{310\xspace}
\newcommand{\MaxCallSitePackageRnd}{2.4K\xspace}
\newcommand{\MaxCallSitePackage}{2,372\xspace}
\newcommand{\OneCallSitePackageRnd}{48\xspace}
\newcommand{\OneCallSitePackage}{48\xspace}
\newcommand{\NoCallSitePackagesRnd}{233\xspace}
\newcommand{\NoCallSitePackages}{233\xspace}

%\input{tag/enrichDataset.tex}
\newcommand{\UndefinedEvalsRnd}{285K\xspace}
\newcommand{\UndefinedEvals}{285,289\xspace}
\newcommand{\PercentUndefinedEval}{3.3\%\xspace}
\newcommand{\UndefinedEvalExpressionsRnd}{262\xspace}
\newcommand{\UndefinedEvalExpressions}{262\xspace}
\newcommand{\UndefinedOutOfCorpusRnd}{0\xspace}
\newcommand{\UndefinedOutOfCorpus}{0\xspace}
\newcommand{\UndefinedOutOfCoprusPercent}{0\%\xspace}
\newcommand{\MaxCallSitesEnrich}{114\xspace}
\newcommand{\OneCallSitesEnrich}{61\xspace}
\newcommand{\NoCallSitesEnrich}{297\xspace}
%\input{tag/patterns.tex}
\newcommand{\PatternLibRnd}{4K\xspace}
\newcommand{\PatternLib}{4,278\xspace}
\newcommand{\PatternLibRatio}{.05\%\xspace}
\newcommand{\PatternLibSourceRnd}{370\xspace}
\newcommand{\PatternLibSource}{370\xspace}
\newcommand{\PatternLibLocalRnd}{100\xspace}
\newcommand{\PatternLibLocal}{100\xspace}
\newcommand{\PatternReadRnd}{59K\xspace}
\newcommand{\PatternRead}{59,776\xspace}
\newcommand{\PatternReadRatio}{.7\%\xspace}
\newcommand{\PatternReadSlotAccessRatio}{88\%\xspace}
\newcommand{\PatternReadDatatableRatio}{27\%\xspace}
\newcommand{\PatternAssignRnd}{68K\xspace}
\newcommand{\PatternAssign}{68,754\xspace}
\newcommand{\PatternAssignRatio}{.9\%\xspace}
\newcommand{\PatternAssignArrowRatio}{18\%\xspace}
\newcommand{\PatternAssignArrowMagrittrRatio}{59\%\xspace}
\newcommand{\PatternAssignSuperarrowRatio}{81\%\xspace}
\newcommand{\PatternAssignSuperarrowPlyrRatio}{99\%\xspace}
\newcommand{\PatternManualPackagesRnd}{20\xspace}
\newcommand{\PatternManualPackages}{20\xspace}
\newcommand{\PatternManualCallsitesRnd}{161\xspace}
\newcommand{\PatternManualCallsites}{161\xspace}

\graphicspath{{img/}}

\lstset{language=R}

\definecolor{LightGray}{rgb}{.92,.92,.92}
\definecolor{Gray}{rgb}{.3,.3,.3}
\definecolor{DarkGray}{rgb}{.5,.5,.5}

\lstset{ %
  columns=flexible,
  captionpos=b,
  frame=single,
  framerule=0pt,
  framexleftmargin=-1mm,
  framexrightmargin=-1mm,
  tabsize=2,
  belowskip=0pt,
  basicstyle=\small\ttfamily,
  backgroundcolor=\color{LightGray},
  emphstyle=\sffamily,
  keywordstyle=\bfseries,
  commentstyle=\color{Gray}\em,
  stringstyle=\color{Gray}
}
\lstdefinestyle{R}{ %
  language=R,
  deletekeywords={new, env, equal, c, runif, trace, args, exp, t, all, get,
    names, is, environment, class, substitute, expression, list, null, Internal,
    sample, diag, length, rep, nrow, stop, offset, pmax, Machine,
    double, parent, frame, par, methods, end, dir, apply, deparse, missing,
    plot, as, integer, character, inherits, numeric, paste, eval, quote, call,
    formula, df, log, sum, c, local, legend, file, scale, round, title, order,
    drop, which, grid, print, ncol, dim, max, format, sort, rug, matrix, start,
    unique, mean, df, attr, do, power, \$},
  otherkeywords={},
  breaklines=true
}

\newcommand{\eg}{\emph{e.g.},\xspace}
\newcommand{\ie}{\emph{i.e.},\xspace}
\newcommand{\cf}{\emph{cf.}\xspace}
\newcommand{\summary}[1]{{\csname #1\endcsname} ({\csname #1Min\endcsname} / {\csname #1Mean\endcsname} / {\csname #1Max\endcsname})}
\newcommand{\summaryrnd}[1]{{\csname #1Rnd\endcsname} ({\csname #1MinRnd\endcsname} / {\csname #1MeanRnd\endcsname} / {\csname #1MaxRnd\endcsname})}

\newcommand{\eval}{\texttt{eval}\xspace}
\newcommand{\evals}{{\sf eval}s\xspace}
\renewcommand{\parse}{\c{parse}}
\newcommand{\source}{\c{source}}
\newcommand{\local}{\c{local}}
\newcommand{\unlockBinding}{\c{unlockBinding}}
\newcommand{\substitute}{\c{substitute}}
\newcommand{\datatable}{\c{data.table}}
\newcommand{\mlogit}{\c{mlogit}}
\newcommand{\mboost}{\c{mboost}}
\newcommand{\metafor}{\c{metafor}}
\newcommand{\lavaan}{\c{lavaan}}
\newcommand{\mclust}{\c{mclust}}
\newcommand{\gamlss}{\c{gamlss}}
\newcommand{\ggproto}{\c{ggproto}}
\newcommand{\ggplot}{\c{ggplot2}}
\newcommand{\base}{\c{base}}
\renewcommand{\c}[1]{\lstinline{#1}\xspace}
\newcommand{\miss}[1]{{\textcolor{red}{#1}}\xspace}
\newcommand{\evil}{\emph{evil}\xspace}
\newcommand{\instrumentr}{\emph{instrumentr}\xspace}
\newcommand{\rdyntrace}{\emph{R-dyntrace}\xspace}
\newcommand{\covr}{\emph{covr}\xspace}
\newcommand{\runr}{\emph{runr}\xspace}

\bibliographystyle{plainurl}% the mandatory bibstyle

@@

\author{Anon}{Under review}{}{}{}
\authorrunning{Anon}
\Copyright{Anon}
\keywords{R, reflection, eval}

%Editor-only macros:: begin (do not touch as author)%%%%%%%%%%%%%%%%%%%%%%%%%%%\
%%%%%%%                                                                         
\EventEditors{Eds.}
\EventNoEds{2}
\EventLongTitle{European Conference on Object Oriented Programming (ECOOP 2021)}
\EventShortTitle{ECOOP 2021}
\EventAcronym{ECOOP}
\EventYear{2021}
\EventDate{December 24--27, 2016}
\EventLocation{Little Whinging, United Kingdom}
\EventLogo{}
\SeriesVolume{42}
\ArticleNo{23}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{CCSXML}
  <ccs2012>
  <concept>
  <concept_id>10011007.10011006.10011050.10010517</concept_id>
  <concept_desc>Software and its engineering~Scripting languages</concept_desc>
  <concept_significance>500</concept_significance>
  </concept>
  <concept>
  <concept_id>10002944.10011123.10010912</concept_id>
  <concept_desc>General and reference~Empirical studies</concept_desc>
  <concept_significance>500</concept_significance>
  </concept>
  <concept>
  <concept_id>10011007.10011006.10011008</concept_id>
  <concept_desc>Software and its engineering~General programming languages</concept_desc>
  <concept_significance>500</concept_significance>
  </concept>
  </ccs2012>
\end{CCSXML}

\ccsdesc[500]{Software and its engineering~Scripting languages}
\ccsdesc[500]{General and reference~Empirical studies}
\ccsdesc[500]{Software and its engineering~General programming languages}

\begin{document}

\maketitle

\begin{abstract}
  \noindent Most dynamic languages allow users to turn text into code
  using various functions, often named \eval, with language-dependent
  semantics. The widespread use of these reflective functions hinders
  static analysis and prevents compilers from performing many
  optimizations. This paper aims to provide a better sense of why
  programmers use \eval.  Understanding how \eval is used in practice
  is key to finding ways to mitigate its negative impact. We have
  reasons to believe that reflective feature usage is language and
  application domain specific. In this paper, we focus on data science
  code written in R, and compare our results to previous work that
  analyzed web programming in JavaScript.  We conduct a large-scale
  study of a corpus of \CorpusAllCodeRnd lines of libraries and
  end-user code on which we performed dynamic analysis to confirm that
  \eval is indeed in widespread use, and categorized patterns of
  usage. We found that \eval is more dangerous in some ways, and safer
  in others, than what was previously reported for JavaScript.
\end{abstract}

@@

Traditional program analysis techniques are based on sound reasoning about
program behavior, a program analyzer computes an over-approximation of the
set of possible operations performed by the system being
analyzed~\cite{cc77}.  This is predicated on knowing the program's code, and
computing that code's behavior for all possible inputs. The presence of
\eval entails that the program's input, any string variable, may be
reflected into its code giving rise to \emph{any} behavior allowed by the
language semantics. In many dynamic languages, \eval can redefine most
user-defined and built-in functions resulting in a complete loss of
precision for any operation following \eval. A group of influential
researchers argued to give up on soundness and, instead, to
under-approximate dynamic features~\cite{soundy} In their words ``a
practical analysis, therefore, may pretend that \eval does nothing, unless
it can precisely resolve its string argument at compile time.''  Assuming
that \eval does not have side-effects may be too optimistic. We rather
propose to study what \eval does in practice, in real-world code, so as to
give researchers data about how to better under-approximate uses of that
feature.

>>>>

\documentclass[USenglish,cleveref, autoref, thm-restate]{lipics-v2019}
\usepackage{listings,hyperref,multirow,paralist,xspace,url}
\input{macro}

@@

\begin{document}\maketitle

\begin{abstract}
  \noindent Most dynamic languages allow users to turn text into code
  using various functions, often named \eval, with language-dependent
  semantics. The widespread use of these reflective functions hinders
  static analysis and prevents compilers from performing many
  optimizations. This paper aims to provide a better sense of why
  programmers use \eval.  Understanding how \eval is used in practice
  is key to finding ways to mitigate its negative impact. We have
  reasons to believe that reflective feature usage is language and
  application domain specific. In this paper, we focus on data science
  code written in R, and compare our results to previous work that
  analyzed web programming in JavaScript.  We conduct a large-scale
  study of a corpus of \CorpusAllCodeRnd lines of libraries and
  end-user code on which we performed dynamic analysis to confirm that
  \eval is indeed in widespread use. We found that \eval is more
  dangerous in some ways, and safer in others, than what was
  previously reported for JavaScript.
\end{abstract}

@@

Most dynamic languages provide their users with a facility to
transform unstructured text into executable code, and to evaluate that
code. In this paper we refer to this reflective facility of a language
as \eval bowing to its origins in LISP in 1956~\cite{lisp}. \Eval has
been much maligned over the years. In computing lore, it is as close
to a boogeyman as it gets. Yet, for McCarthy, \eval was simply the way
to write down the definition of LISP, he was surprised that someone
coded it up and offered it end users.  Since then, reflective
facilities have been used to parameterize programs over code patterns
that can be provided after the program is written, when it
executes. The presence of such a feature in a language is a hallmark
of dynamism as it is a form of delayed binding.

\vspace{2mm}\noindent\emph{Trouble in Paradise.} Reflective facilities
hinder most attempt to reason about the code using them, as well as to
apply meaning-preserving program transformations. In practice this
means that static analysis techniques will loose so much precision as
to become pointless and that anything but the most trivial, local,
compiler optimizations will be unsound. Furthermore the addition of
new code --code that could have been obtained from a network
connection-- as the program is running is a security vulnerability
waiting to happen.
